\documentclass[10pt, aspectratio=149]{beamer}
\usetheme{metropolis}
\usepackage{appendixnumberbeamer}

% Set dark mode color theme
\metroset{background=dark}

\usepackage{libertine}

% Customize the title page
\title{Enhancing Google Maps: Three Persona Perspectives}
\date{\today}
\author{Hemant K}
\institute{NextLeap Product Manager Fellow}


% Add a table of contents slide
\AtBeginSection[]
{
  \begin{frame}{Outline}
    \tableofcontents[currentsection]
  \end{frame}
}

%%-----------------------------------------------------------------------------

\begin{document}

\maketitle

\begin{frame}{Outline}
  \tableofcontents
\end{frame}

\section{Introduction}

\begin{frame}{Introduction}
  \begin{itemize}
    \item Welcome to the presentation on enhancing Google Maps.
    \item We will explore improvements from three different persona perspectives.
  \end{itemize}
\end{frame}

\section{Persona 1: Commuter Krish}

\begin{frame}{Persona 1: Commuter Krish}
  \begin{itemize}
    \item Persona: Commuter Krish
    \item Challenges faced by Krish during daily commutes.
    \item Features and improvements tailored for Krish.
  \end{itemize}
\end{frame}

\begin{frame}{Challenges of Commuter Krish}
  \begin{itemize}
    \item Long daily commutes in heavy traffic.
    \item Frequent delays and route changes.
    \item Desire for more accurate ETAs and alternative routes.
  \end{itemize}
\end{frame}

\begin{frame}{Enhancements for Krish}
  \begin{itemize}
    \item Real-time traffic updates with predictive analysis.
    \item Improved route suggestions based on historical data.
    \item Voice-activated navigation for hands-free use.
  \end{itemize}
\end{frame}

\section{Persona 2: Explorer Alida}

\begin{frame}{Persona 2: Explorer Alida}
  \begin{itemize}
    \item Persona: Explorer Alida
    \item How Alida uses Google Maps for travel and exploration.
    \item Features and enhancements that can enhance her experience.
  \end{itemize}
\end{frame}

\begin{frame}{Exploration Needs of Alida}
  \begin{itemize}
    \item Frequent traveler and explorer.
    \item Interest in discovering local attractions and hidden gems.
    \item Desire for personalized travel recommendations.
  \end{itemize}
\end{frame}

\begin{frame}{Enhancements for Alida}
  \begin{itemize}
    \item Personalized travel itineraries based on interests.
    \item Local tips and recommendations from fellow travelers.
    \item Augmented reality (AR) city tours for immersive experiences.
  \end{itemize}
\end{frame}

\section{Persona 3: Business Owner Vishnu}

\begin{frame}{Persona 3: Business Owner Vishnu}
  \begin{itemize}
    \item Persona: Business Owner Vishnu
    \item Vishnu's perspective on Google Maps as a local business owner.
    \item Ideas for improving business-related features and listings.
  \end{itemize}
\end{frame}

\begin{frame}{Business Perspective of Vishnu}
  \begin{itemize}
    \item Local business owner seeking online visibility.
    \item Importance of accurate business listings and reviews.
    \item Desire for tools to engage with and attract customers.
  \end{itemize}
\end{frame}

\begin{frame}{Enhancements for Vishnu}
  \begin{itemize}
    \item Simplified tools for business owners to update listings.
    \item Enhanced review management and feedback analytics.
    \item Promotional features and real-time offers for businesses.
  \end{itemize}
\end{frame}

\section{Conclusion}

\begin{frame}{Conclusion}
  \begin{itemize}
    \item Insights from Commuter Krish, Explorer Alida, and Business Owner Vishnu.
    \item User-centric approach to Google Maps enhancement.
  \end{itemize}
\end{frame}

\appendix
\section*{Additional Slides}

\begin{frame}{Additional Slides}
  Thank You
\end{frame}
%%-----------------------------------------------------------------------------

\end{document}
